Differentiable Neural Computers

### 2018-05-04 Presentation/Presentation.tex
LSTM slide

\begin{frame}{Controller}
	A deep \alert{long short-term memory network} receiving 
	\[
	\xx_t=[ \pmb{x}_t; \pmb{r}_{t-1}^1; \dots \pmb{r}_{t-1}^R]
	\]
	and producing 
	\[
	(\pmb{v}_t,\pmb{\xi}_t)=\mathcal{N}([\xx_1;\dots;\xx_T];\theta)
	\]
	where $\mathcal{N}$ a set of state equations and $\theta$ their trainable parameters.
\end{frame}

@@

\begin{frame}{Controller}
	\begin{figure}
	\begin{tikzpicture}[scale=0.5]
		% LSTM
		% outer box
		\draw[thick] (0,0) |- (18,12);
		\draw[thick] (18,12) |- (0,0);
		% core nodes
		\node (s) at (9,6) {$s$};
		\node (fx) at (9,4) {$x$};
		\node (f) at (9,2) {$f$};
		\node (i) at (6,8) {$i$};
		\node (ix) at (6,6) {$x$};
		\node (id) at (4,6) {$S$};
		\node (o) at (12,10) {$o$};
		\node (ox) at (16,6) {$x$};
		\node (od) at (12,6) {$S$};
		% recurrency
		\draw (f) -| (2,6);
		\draw (2,6) |- (o);
		% gates
		\draw (o) edge (ox);
		\draw (i) edge (ix);
		\draw (s) edge[bend right=90] (fx);
		\draw (s) edge[bend left=90] (fx);
		\draw (f) edge (fx);
		% forward
		\draw (0,6) edge (9,6);
		\draw (s) edge (od);
		\draw (od) edge (18,6);
		\end{tikzpicture}
	\end{figure}
\end{frame}
\end{document}

>>>>

\begin{frame}{Controller}
	A deep \alert{long short-term memory network} receiving 
	\[
	\xx_t=[ \pmb{x}_t; \pmb{r}_{t-1}^1; \dots ;\pmb{r}_{t-1}^R]
	\]
	and producing 
	\[
	(\pmb{v}_t,\pmb{\xi}_t)=\mathcal{N}([\xx_1;\dots;\xx_T];\theta)
	\]
	where $\mathcal{N}$ a set of state equations and $\theta$ their trainable parameters.
\end{frame}

@@

\begin{frame}{Controller}
	\alert{Single LSTM Layer}
	\begin{figure}
	\begin{tikzpicture}[scale=0.5]
		%-------------------------------------------------------------------------------
		% LSTM
		%-------------------------------------------------------------------------------
		\node[circle, inner sep=0pt,minimum size=3mm,fill=white] (conc) 
			at (-0,6) {\textcolor{mDarkTeal}{$;$}};

		% outer box
		\draw[densely dotted, thick, gray!90] (18,6) -| (18,12);
		\draw[densely dotted, thick,->, gray!90] (18,12) -| (conc);
		%\draw[thick] (0,0) |- (18,12);
		%\draw[thick] (18,12) |- (0,0);

		% core nodes
		\node[circle, inner sep=0pt,minimum size=3mm,fill=white] (conc) 
			at (-0,6) {\textcolor{mDarkTeal}{$;$}};
		\node[circle, draw=black, thick, inner sep=0pt,minimum size=6mm,fill=white] (s) 
			at (9,6) {\large\textcolor{black}{$\Ss_t$}};
		\node[circle, inner sep=0pt,minimum size=3mm,fill=white] (fx) 
			at (9,4) {\textcolor{mDarkTeal}{$\times$}};
		\node[circle, draw=black, thick, inner sep=0pt,minimum size=6mm,fill=white] (f) 
			at (9,2) {\large\textcolor{black}{$\ff_t$}};
		\node[circle, draw=black, thick, inner sep=0pt,minimum size=6mm,fill=white] (i) 
			at (6,8) {\large\textcolor{black}{$\ii_t$}};
		\node[circle, inner sep=0pt,minimum size=3mm,fill=white] (ix) 
			at (6,6) {\textcolor{mDarkTeal}{$\times$}};
		\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (id) 
			at (4,8) {\textcolor{mDarkTeal}{$\int$}};
		\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (sd) 
			at  (4,6) {\small\textcolor{mDarkTeal}{$\int$}};
		\node[circle, draw=black, thick, inner sep=0pt,minimum size=6mm,fill=white] (o) 
			at (12,10) {\large\textcolor{black}{$\oo_t$}};
		\node[circle, inner sep=0pt,minimum size=3mm,fill=white] (ox) 
			at (16,6) {\textcolor{mDarkTeal}{$\times$}};
		\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (od) 
			at (12,6) {\small\textcolor{mDarkTeal}{$\int$}};
		\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (odd) 
			at (4,10) {\small\textcolor{mDarkTeal}{$\int$}};
		\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (fd) 
			at (4,2) {\small\textcolor{mDarkTeal}{$\int$}};
		% recurrency
		\draw (f) edge[thick] (fd);
		\draw[thick] (fd) -| (2,6);
		\draw[thick] (2,6) |- (odd);
		\draw (odd) edge[->,thick] (o);
		\draw[thick] (2,6) |- (id);
		\draw (id) edge[thick] (i);
		% gates
		\draw (o) edge[->, thick] (ox);
		\draw (i) edge[->, thick] (ix);
		\draw (s) edge[->,bend right=45, thick, densely dotted, gray!90] (fx);
		\draw (s) edge[<-,bend left=45, thick] (fx);
		\draw (f) edge[->, thick] (fx);
		% forward
		\draw(-2,6) edge[thick] (conc);
		\draw (0,6) edge[thick] (sd);
		\draw (sd) edge[->, thick] (ix);
		\draw (ix) edge[->, thick] (s);
		\draw (s) edge[thick] (od);
		\draw (od) edge[->, thick] (ox);
		\draw (ox) edge[->, thick] (20,6);

		% labels
		\node[label=above:$\textcolor{white}{\xx_t}$] (x) at (-1,6) {};
		\node[label=above:$\textcolor{white}{\hh_t}$] (ht) at (19.5,6) {};
		\node[label=above:$\textcolor{white}{\hh_{t-1}}$] (x) at (9,12) {};
		\end{tikzpicture}
	\end{figure}
\end{frame}
\end{document}
